Hand picking similar behaving group of customers to check clustering results

### 2021-08-18 supplementary/algorithm4/real-data/handpick-18.Rmd
simulated and real data results update for algorithm 3

```{r hand-pick}

@@

# 
# group2_data%>% 
#   ungroup() %>% 
#   filter(design==1) %>% 
#   #filter(customer_id %in% c(8148781, 10703878)) %>% 
#   ggplot(aes(x = as.integer(hour_day), y = median_kwh)) +
#   geom_line(size = 0.5) +
#   facet_wrap(~customer_id, scales = "free_y") + theme_minimal()+ theme(strip.text.y = element_text(size = 5))
# 
# 
# group2_data%>% 
#   ungroup() %>% 
#   filter(design==2) %>% 
#   #filter(customer_id %in% c(8148781, 10703878)) %>% 
#   ggplot(aes(x = as.integer(hour_day), y = median_kwh)) +
#   geom_line(size = 0.5) +
#   facet_wrap(~customer_id, scales = "free_y") + theme_minimal()+ theme(strip.text.y = element_text(size = 5))
```

@@

data_heatmap %>% 
  ggplot(aes(x = as.integer(category))) + 
  geom_ribbon(aes(ymin = `25%`, 
                  ymax = `75%`), fill = "lightblue") +
  geom_line(aes(y = `50%`), size = 0.7) +
  facet_wrap(design~customer_id, 
             scales = "free_y", 
             labeller = "label_value",
             ncol = 6) +
  theme_bw() +
    theme(strip.text = element_text(size = 10, margin = margin(b = 0, t = 0))) + xlab("hour-of-day") + ylab("demand (in Kwh)")
```
# quantile_prob_val = c(0.5, 0.75)

## only hod

```{r,echo = TRUE}
quantile_prob_val = c(0.5, 0.75)
#data_pick <- data_pick %>% filter(!(customer_id %in% c(8485375, 8952846)))
library(gracsr)
v2 <- suppressWarnings(
  scaled_dist_gran(data_pick, "hour_day", 
                   response = "general_supply_kwh",
                   quantile_prob_val = quantile_prob_val)) %>% rename("dist_hod" = "dist")
v3 <- suppressWarnings(
  scaled_dist_gran(data_pick, "day_month",
                   response = "general_supply_kwh", 
                   quantile_prob_val = quantile_prob_val)) %>% rename("dist_dom" = "dist")

data_dist <- v3 %>% 
  left_join(v2) %>%
  mutate(dist = dist_hod) %>% 
    pivot_wider(-c(3, 4), 
                names_from = customer_to,
              values_from = dist) %>%
  rename("customer_id" = "customer_from")
```

```{r}
d = stats::as.dist(data_dist[,-1])
hc = stats::hclust(d,method="complete")

groups <- tibble(group = cutree(hc, k=3), customer_id = data_dist$customer_id)
groups %>% group_by(group) %>% summarise(n=n())
#groups %>% filter(group==1)
#groups %>% filter(group==2)
#groups %>% filter(group==3)

data_heatmap_new <- data_heatmap %>% left_join(groups)

data_heatmap_new$group = as.factor(data_heatmap_new$group)

data_heatmap_new %>% 
  ggplot(aes(x = as.integer(category))) + 
  geom_ribbon(aes(ymin = `25%`, 
                  ymax = `75%`), fill = "lightblue") +
  geom_line(aes(y = `50%`, color = group), size = 0.7) +
  facet_wrap(group~customer_id, 
             scales = "free_y", 
             labeller = "label_value",
             ncol = 6) +
  theme_bw() +
    theme(strip.text = element_text(size = 10, margin = margin(b = 0, t = 0))) + xlab("hour-of-day") + ylab("demand (in Kwh)") +
  scale_color_brewer(palette = "Dark2")

## hod + dom

```{r,echo = TRUE}
#data_pick <- data_pick %>% filter(!(customer_id %in% c(8485375, 8952846)))
library(gracsr)
v2 <- suppressWarnings(
  scaled_dist_gran(data_pick, "hour_day", 
                   response = "general_supply_kwh",
                   quantile_prob_val = quantile_prob_val)) %>% rename("dist_hod" = "dist")
v3 <- suppressWarnings(
  scaled_dist_gran(data_pick, "day_month",
                   response = "general_supply_kwh", 
                   quantile_prob_val = quantile_prob_val)) %>% rename("dist_dom" = "dist")

data_dist <- v3 %>% 
  left_join(v2) %>%
  mutate(dist = dist_hod + dist_dom) %>% 
    pivot_wider(-c(3, 4), 
                names_from = customer_to,
              values_from = dist) %>%
  rename("customer_id" = "customer_from")
```

```{r}
d = stats::as.dist(data_dist[,-1])
hc = stats::hclust(d,method="complete")

groups <- tibble(group = cutree(hc, k=3), customer_id = data_dist$customer_id)
groups %>% group_by(group) %>% summarise(n=n())
#groups %>% filter(group==1)
#groups %>% filter(group==2)
#groups %>% filter(group==3)

data_heatmap_new <- data_heatmap %>% left_join(groups)

data_heatmap_new$group = as.factor(data_heatmap_new$group)

data_heatmap_new %>% 
  ggplot(aes(x = as.integer(category))) + 
  geom_ribbon(aes(ymin = `25%`, 
                  ymax = `75%`), fill = "lightblue") +
  geom_line(aes(y = `50%`, color = group), size = 0.7) +
  facet_wrap(group~customer_id, 
             scales = "free_y", 
             labeller = "label_value",
             ncol = 6) +
  theme_bw() +
    theme(strip.text = element_text(size = 10, margin = margin(b = 0, t = 0))) + xlab("hour-of-day") + ylab("demand (in Kwh)") +
  scale_color_brewer(palette = "Dark2")

# quantile_prob_val = seq(0.1, 0.9, 0.1)

## only hod

```{r,echo = TRUE}
quantile_prob_val = seq(0.1, 0.9, 0.1)
#data_pick <- data_pick %>% filter(!(customer_id %in% c(8485375, 8952846)))
library(gracsr)
v2 <- suppressWarnings(
  scaled_dist_gran(data_pick, "hour_day", 
                   response = "general_supply_kwh",
                   quantile_prob_val = quantile_prob_val)) %>% rename("dist_hod" = "dist")
v3 <- suppressWarnings(
  scaled_dist_gran(data_pick, "day_month",
                   response = "general_supply_kwh", 
                   quantile_prob_val = quantile_prob_val)) %>% rename("dist_dom" = "dist")

data_dist <- v3 %>% 
  left_join(v2) %>%
  mutate(dist = dist_hod) %>% 
    pivot_wider(-c(3, 4), 
                names_from = customer_to,
              values_from = dist) %>%
  rename("customer_id" = "customer_from")
```

```{r}
d = stats::as.dist(data_dist[,-1])
hc = stats::hclust(d,method="complete")

groups <- tibble(group = cutree(hc, k=3), customer_id = data_dist$customer_id)
groups %>% group_by(group) %>% summarise(n=n())
#groups %>% filter(group==1)
#groups %>% filter(group==2)
#groups %>% filter(group==3)

data_heatmap_new <- data_heatmap %>% left_join(groups)

data_heatmap_new$group = as.factor(data_heatmap_new$group)

data_heatmap_new %>% 
  ggplot(aes(x = as.integer(category))) + 
  geom_ribbon(aes(ymin = `25%`, 
                  ymax = `75%`), fill = "lightblue") +
  geom_line(aes(y = `50%`, color = group), size = 0.7) +
  facet_wrap(group~customer_id, 
             scales = "free_y", 
             labeller = "label_value",
             ncol = 6) +
  theme_bw() +
    theme(strip.text = element_text(size = 10, margin = margin(b = 0, t = 0))) + xlab("hour-of-day") + ylab("demand (in Kwh)") +
  scale_color_brewer(palette = "Dark2")

## hod + dom

```{r,echo = TRUE}
#data_pick <- data_pick %>% filter(!(customer_id %in% c(8485375, 8952846)))
library(gracsr)
v2 <- suppressWarnings(
  scaled_dist_gran(data_pick, "hour_day", 
                   response = "general_supply_kwh",
                   quantile_prob_val = quantile_prob_val)) %>% rename("dist_hod" = "dist")
v3 <- suppressWarnings(
  scaled_dist_gran(data_pick, "day_month",
                   response = "general_supply_kwh", 
                   quantile_prob_val = quantile_prob_val)) %>% rename("dist_dom" = "dist")

data_dist <- v3 %>% 
  left_join(v2) %>%
  mutate(dist = dist_hod + dist_dom) %>% 
    pivot_wider(-c(3, 4), 
                names_from = customer_to,
              values_from = dist) %>%
  rename("customer_id" = "customer_from")
```

```{r}
d = stats::as.dist(data_dist[,-1])
hc = stats::hclust(d,method="complete")

groups <- tibble(group = cutree(hc, k=3), customer_id = data_dist$customer_id)
groups %>% group_by(group) %>% summarise(n=n())
#groups %>% filter(group==1)
#groups %>% filter(group==2)
#groups %>% filter(group==3)

data_heatmap_new <- data_heatmap %>% left_join(groups)

data_heatmap_new$group = as.factor(data_heatmap_new$group)

data_heatmap_new %>% 
  ggplot(aes(x = as.integer(category))) + 
  geom_ribbon(aes(ymin = `25%`, 
                  ymax = `75%`), fill = "lightblue") +
  geom_line(aes(y = `50%`, color = group), size = 0.7) +
  facet_wrap(group~customer_id, 
             scales = "free_y", 
             labeller = "label_value",
             ncol = 6) +
  theme_bw() +
    theme(strip.text = element_text(size = 10, margin = margin(b = 0, t = 0))) + xlab("hour-of-day") + ylab("demand (in Kwh)") +
  scale_color_brewer(palette = "Dark2")

## remove the outlier and run again

```{r,echo = TRUE}
quantile_prob_val = c(0.5, 0.75)
data_pick <- data_pick %>% filter(!(customer_id %in% 8952846))
library(gracsr)
v2 <- suppressWarnings(
  scaled_dist_gran(data_pick, "hour_day", 
                   response = "general_supply_kwh",
                   quantile_prob_val = quantile_prob_val)) %>% rename("dist_hod" = "dist")
v3 <- suppressWarnings(
  scaled_dist_gran(data_pick, "day_month",
                   response = "general_supply_kwh", 
                   quantile_prob_val = quantile_prob_val)) %>% rename("dist_dom" = "dist")

data_dist <- v3 %>% 
  left_join(v2) %>%
  mutate(dist = dist_hod + dist_dom) %>% 
    pivot_wider(-c(3, 4), 
                names_from = customer_to,
              values_from = dist) %>%
  rename("customer_id" = "customer_from")
```

```{r}
d = stats::as.dist(data_dist[,-1])
hc = stats::hclust(d,method="complete")

groups <- tibble(group = cutree(hc, k=3), customer_id = data_dist$customer_id)
groups %>% group_by(group) %>% summarise(n=n())
#groups %>% filter(group==1)
#groups %>% filter(group==2)
#groups %>% filter(group==3)

data_heatmap_new <- data_heatmap %>% filter(customer_id!=8952846) %>% left_join(groups)

data_heatmap_new$group = as.factor(data_heatmap_new$group)

data_heatmap_new %>% 
  ggplot(aes(x = as.integer(category))) + 
  geom_ribbon(aes(ymin = `25%`, 
                  ymax = `75%`), fill = "lightblue") +
  geom_line(aes(y = `50%`, color = group), size = 0.7) +
  facet_wrap(group~customer_id, 
             scales = "free_y", 
             labeller = "label_value",
             ncol = 6) +
  theme_bw() +
    theme(strip.text = element_text(size = 10, margin = margin(b = 0, t = 0))) + xlab("hour-of-day") + ylab("demand (in Kwh)") +
  scale_color_brewer(palette = "Dark2")

>>>>

```{r hand-pick}
quantile_prob_val = seq(0.1, 0.9, 0.1)

@@

@@

data_heatmap %>% 
  ggplot(aes(x = as.integer(category))) + 
  geom_ribbon(aes(ymin = `25%`, 
                  ymax = `75%`), fill = "lightblue") +
  #geom_smooth(aes(y = `50%`)) +
  geom_line(aes(y = `50%`), size = 0.7) +
    facet_wrap(design~customer_id, 
             scales = "free_y", 
             labeller = "label_value",
             ncol = 6) +
  theme_bw() +
    theme(strip.text = element_text(size = 10, margin = margin(b = 0, t = 0))) + xlab("hour-of-day") + ylab("demand (in Kwh)")

data_heatmap %>% 
  ggplot(aes(x = as.integer(category))) + 
  geom_ribbon(aes(ymin = `25%`, 
                  ymax = `75%`), fill = "lightblue") +
  geom_smooth(aes(y = `50%`)) +
  #geom_line(aes(y = `50%`), size = 0.7, color = "orange") +
    facet_wrap(design~customer_id, 
             scales = "free_y", 
             labeller = "label_value",
             ncol = 6) +
  theme_bw() +
    theme(strip.text = element_text(size = 10, margin = margin(b = 0, t = 0))) + xlab("hour-of-day") + ylab("demand (in Kwh)")
```
```{r,echo = TRUE}
#data_pick <- data_pick %>% filter(!(customer_id %in% c(8485375, 8952846)))
library(gracsr)
v2 <- suppressWarnings(
  dist_pairwise_clust(data_pick, "hour_day", 
                   response = "general_supply_kwh",
                   quantile_prob_val = c(0.5, 0.75))) 
v3 <- suppressWarnings(
  dist_pairwise_clust(data_pick, "day_month",
                   response = "general_supply_kwh", 
                   quantile_prob_val = c(0.5, 0.75)))

data_dist <- v %>%
    pivot_wider(
  names_from = customer_to,
values_from = dist) %>%
rename("customer_id" = "customer_from")
```

```{r}
d = as.dist(v3[,-1])
hc = stats::hclust(d,method="complete")

groups <- tibble(group = cutree(hc, k=3), customer_id = v2$customer_id)
groups %>% group_by(group) %>% summarise(n=n())
groups %>% filter(group==1)
groups %>% filter(group==2)
groups %>% filter(group==3)
```
